---
title: "Daily Turbidity Summaries"
author: "California Department of Water Resources"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
#opts_knit$set(root.dir = "C:/Users/rhartman/OneDrive - California Department of Water Resources/smelt #cages/SMTWaterQuality/docs")
library(tidyverse)
library(lubridate)
library(cder)
library(sf)
load("GISdata.RData")
```

## Daily average turbidities

This is a summary of daily average turbidity for several stations in the Delta.


```{r stations, echo=FALSE, warning=FALSE, message=FALSE}

ggplot()+
  geom_sf(data = WW_Delta, fill = "lightblue", color = "grey")+
  geom_sf(data = stations)+
  geom_sf_text(data = stations, aes(label = StationCode), nudge_x = .01, nudge_y = .01, size = 2)+
  coord_sf(ylim = c(37.8, 38.1), xlim = c(-121.75, -121.3))+
  theme_bw()

```

## Here is the average turbidity for the past 7 days

(all stations combined, first turbidity, then secchi)

```{r turbidity, echo=FALSE, warning=FALSE, message=FALSE}
load("TurbToSecchi.RData")
turb = cdec_query(stations$StationCode, c(27,221), duration = "E",
                  start.date = today()-7, end.date = today())

#calculate daily average by station
turb2 = mutate(turb, Date = date(DateTime)) %>%
  group_by(Date, StationID) %>%
  summarize(Turbidity = mean(Value, na.rm =T))

#now daily average across stations
turb3 = turb2 %>%
  group_by(Date) %>%
  summarize(Turbidity = mean(Turbidity, na.rm =T))

#plot it
ggplot(turb3, aes(x = Date, y = Turbidity))+ geom_line()+geom_point()+
  geom_text(aes(label = round(Turbidity)), nudge_y = 1, size = 5)+
  ylab("Turbidity (NTU)")+ theme_bw()

ggplot(turb3, aes(x = Date, y = TurbToSecchi(Turbidity))) + geom_line()+geom_point()+
  geom_text(aes(label = round(TurbToSecchi(Turbidity))), nudge_y = 5, size = 5)+
  ylab("Estimated Secchi Depth, CM")+ theme_bw()

```

Here are the daily averages from the individual stations. 

```{r turbidityall, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(turb2, aes(x = Date, y = Turbidity)) + geom_line()+geom_point()+
  facet_wrap(~StationID)+
  geom_text(aes(label = round(Turbidity)), nudge_y = 1, size = 3)+
  ylab("Turbidity (NTU)")+ theme_bw()

```

Here it is converted to secchi depth

```{r secchi, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(turb2, aes(x = Date, y = TurbToSecchi(Turbidity))) + geom_line()+geom_point()+
  facet_wrap(~StationID)+
  geom_text(aes(label = round(TurbToSecchi(Turbidity))), nudge_y = 5, size = 3)+
  ylab("Estimated Secchi Depth, CM")+theme_bw()

```

### A note on secchi conversions

Turbidity and secchi depth have a pretty good correlation when both are log-transformed. However, secchi depth is subject to some degree of variability with observer, weather, time of day, waves, and whether the observer has had their coffee. Turbidity, as measured by a sonde, is also subject to some variability depending on when the sonde was last calibrated.

To convert between turbidity and secchi depth for the purpose of this document, we used secchi depth data from an integrated dataset of discrete water quality (Bashevkin et al, 2013), collected by IEP surveys from 2010-2022 for the South Delta (area shown in map above). The secchi depths were matched to the nearest continuous station's daily average turbidity. Data is available on GitHub here: [discretewq](https://github.com/InteragencyEcologicalProgram/discretewq)

We then log-transformed secchi depth and turbidity and conducted a linear regression.

```{r, echo = FALSE, warning=FALSE, message=FALSE}

ggplot(filter(WQx2a, ContStation != "OBI", ContStation != "FRK"), aes(x = log(Secchi), y = log(TurbiditySonde))) + geom_point()+
  ylab("Log of Turbidity")+ xlab("Log of Secchi Depth") + geom_smooth(method = "lm")+ theme_bw()


```

We used this regression to estimate the secchi depth given the turbidity from the continuous sondes.

Here's the formula:

Secchi = exp(`summary(convert3)$coefficients[2,1]`*log(Turbidity) +`summary(convert3)$coefficients[1,1]`)


Here is the model output:
```{r}

summary(convert3)
```
When we use this formula to predict secchi depth, we see that it fits reasonably well (r2 of `summary(convert3)$r.squared`) for secchi depths of between 50 and 200, but does less well in clear water and very turbid water due to the log-log relationship between turbidity and secchi. It also does not predict secchi depth in Franks Tract or near OBI very well.

```{r}
ggplot(WQx2a, aes(x = Secchi, y = SecchiPredicted))+ geom_point(aes(color = ContStation))+ 
  scale_color_manual(values = mypal, name = "Continuous\nStation")+
  geom_abline(slope =1, intercept =0, size =1, linetype = 2)+
  theme_bw()+
  annotate("text", x = 300, y = 310, angle = 30, label = "1:1 line")
```


For all the code behind this analysis, please see: 

https://github.com/EMRR-DISE/SMTWaterQuality 
